Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-15 manuscripts/paper-1/main.tex
Results are done

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cleveref}
\usepackage{tabularray}
\usepackage{dirtree,array}

@@

    \subsection{Manual Artifact Reviews}
    During the initial stages of the project, when the target system was not yet available,
    there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included, audits, inspections, reviews, structural analysis and walkthroughs 
    with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}.

@@

    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free regarding fact or truth. 
    In the context of the digital twins, the fact or truth is the real system hence, correctness is a grade of quality, 
    that indicates an error between the real system and a digital twin system.
    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.

    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts of both systems\cite{OxfordDictionary}.

    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. 
    Low fidelity indicates a simplified representation, while high fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
    The concept of fidelity has garnered significant attention in recent
    years and continues to be an important focus in Digital Twin research\cite{Review2}\cite{Review1}.

    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. Therefore, efficiency is achieving
    maximum productivity with minimum wasted effort or expense. It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
    although it differs from the latter's definition, which is defined as the ability to produce large amounts of goods\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}.

@@

    \begin{figure}[htbp]
        \includegraphics[scale = 0.35]{RequirementSpecifications.png}
        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}
        \label{fig:Method}
    \end{figure}

@@

    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified, listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Table~\ref{tab:Table2})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 24\% of the quality issues of the digital twin were related to the correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
    and finally, 28\% were related to evolvability.

@@

    ~\label{tab:Table2}
    ~\caption{Findings from each Artifact}
    \begin{tabular}{lrr}
        \toprule
        \textbf{Artifact Tree}\\
        \midrule
        \DTsetlength{0.2em}{0.5em}{0.5em}{0.4pt}{1pt}
        \begin{minipage}{5cm}\dirtree{%

@@

        .2 Requirement Specification.

@@

        \end{minipage}
    %TODO BETTER TABLE
    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped, the "artifact.qualityattribute.value" is incremented by 1. }
    \renewcommand{\arraystretch}{1.25}
    \scalebox{0.70}{
    \begin{tabular}{l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l}
        \textbf{Findings} & \textbf{Correctness} & \textbf{Completeness} & \textbf{Fidelity} & \textbf{Efficiency} & \textbf{Evolvability}\\
        \textbf{Finding 1} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 2} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 3} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 4} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 5} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 6} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 7} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 8} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 9} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 10} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 11} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 12} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 13} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 14}&~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 15} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 16} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 17} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 18} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 19} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 20} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 21} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Total} &~~~~~~~~~9~~~~~~~~~ & ~~~~~~~~~13~~~~~~~~~ & ~~~~~~~~~3~~~~~~~~~ & ~~~~~~~~~2~~~~~~~~~ & ~~~~~~~~~11~~~~~~~~~ \\

@@

    \begin{figure}[htbp]
        \includegraphics[scale = 0.40]{quality_inspection_results_with_artifacts.png}
        \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in \ref{section:Artifacts}, Y-Axis represents the number of missing quality attributes found for each artifact, 
        and lastly, each digital twin quality attribute is shown by the colors.}
        \label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

@@

    The quality assessment of the digital twin encountered some limitations due to the exility of information about the real system. Some artifacts provided less information, 
    such as process videos, which only provide a limited perspective of the shop floor based on the camera's field of view and the skills of the video maker. 
    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues \ref{fig:QualityInspectonResultsWithArtifacts}.

    The reason of why the  most of the issues are related to the evolvability, 
    completeness and correctness, and less for fidelity and efficiency is due to the stage that the FELICE project is in. Not only the exility of the information is the limiting factor, also the visibility of the information 
    is also an interesting factor. Therefore, evolvability, completeness and correctness are easier to map and detect , rather than fidelity and efficiency.

>>>>

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{float}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cleveref}
\usepackage{tabularray}
\usepackage{dirtree,array}
\usepackage{subcaption}

@@

    \subsection{Manual Artifact Reviews}
    During the initial stages of the project, when the target system was not yet available,
    there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included, audits, inspections, reviews, structural analysis and walkthroughs 
    with the project partners which was inspired by Balci's manual review works~\cite{balcitechniques}.

@@

    \textbf{Correctness} is a  derived word from the adjective \textit{correct}, which means that the entity is error-free regarding fact or truth. 
    In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}). This 
    Meanwhile, the quality of being \textit{correct} is described by the term accuracy \cite{OxfordDictionary}.

    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

    \begin{figure}

        \centering
            \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
            \caption{Correctness and Completeness}\label{fig:CorrectnessAndCompleteness}
    \end{figure}

    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. 
    Low fidelity indicates a simplified representation, 
    while high fidelity refers to an accurate and detailed representation of the real system~\cite{Review2} (Figure~\ref{fig:EfficiencyandFidelity}). 
    The concept of fidelity has garnered significant attention in recent
    years and continues to be an important focus in Digital Twin research\cite{Review2}\cite{Review1}.

    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. 
    Therefore, efficiency is achieving maximum productivity with minimum wasted effort or expense (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
    although it differs from the latter's definition, which is defined as the ability to produce large amounts of goods\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Efficiency and Fidelity}~\label{fig:EfficiencyandFidelity}
    \end{figure}

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a neccessaryy resource to initiate transformation
    within the system (Figure~\ref{fig:Evolvability}).

    \begin{figure}[htbp]
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability}
        ~\label{fig:Evolvability}
    \end{figure}

@@

    \begin{figure}[htbp]
        \includegraphics[scale = 0.30]{RequirementSpecifications.png}
        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}
        \label{fig:Method}
    \end{figure}

@@

    %TODO REWRITE HERE FOR NOVELTY
    First, to assess digital twin quality,
    manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified,
    listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process 
    revealed that a total of thirty-eight digital twin quality attributes were 
    lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
    which indicates an error between the real- and digital twin system. 36\%  were related to completeness, 
    proving that some necessary or appropriate parts were missing.
    8\%  were related to fidelity, indicating a lack of detail. 
    5\%  were related to efficiency, indicating poor performance or excessive resource usage.
    and finally, 28\% were related to evolvability, indicating that the system was unresponsive to the environment and was not flexible or scalable.

    \subsection{Example Findings}  
    Two examples(Finding 12, Finding 18) are given to the reader o illustrate 
    the results of the manual review as well as the mapping to the digital twin quality attributes.

    \subsubsection{Conceptual Model-Finding 12}

    The duration of the micro-operations in the conceptual model was calculated using a simple calculation 
    scheme based on the duration of the corresponding macro-operations,
     which were well-known from a prior well-conducted study. 
    However, relying on estimated, 
    simplified calculations for the micro-operation durations,
    suggests that the digital twin conceptual model suffers from issues of correctness and completeness(Table~\ref{tab:Table1}) .

    \subsubsection{Simulation Model-Finding 18 }
        The discrete event simulation model enforced a strictly sequential execution of micro-operations,
        which precludes the support of parallel execution. 
        However, machine-human collaboration on a task, needs a parallel execution, especially when the cobot overtakes certain micro-operations. 
        Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
        at the same time using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .

    \begin{figure}[htbp]
            \centering
            \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section~\ref{section:Artifacts}, 
            Y-Axis represents the number of missing quality attributes found for each artifact, 
            and lastly, each digital twin quality attribute is shown by the colors.}
            \label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

@@

    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped shown by `X'.}
    \scalebox{0.80}{
        \begin{tabular}{llllll}
            \multicolumn{1}{c}{\textbf{Findings}} & \multicolumn{1}{c} {\textbf{Correctness}} & \multicolumn{1}{c}{\textbf{Completeness}} 
            & \multicolumn{1}{c}{\textbf{Fidelity}} & \multicolumn{1}{c}{\textbf{Efficiency}} & \multicolumn{1}{c}{\textbf{Evolvability}} \\
            \begin{minipage}{4cm}\dirtree{%

@@

                .2 Requirement Specs.

@@

            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 \empty.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .2 \empty.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 \empty.
                .2 \empty.
                .3 ~~~~~X.
                .2 \empty.
                .3 ~~~~~X.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 \empty.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 \empty.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~0.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 \empty.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .2 \empty.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~0.
                .3 ~~~~~0.
                .3 ~~~~~X.
                .3 ~~~~~X.
                .3 ~~~~~x.
            }\end{minipage}

@@

@@

    The quality assessment of the digital twin encountered limitations due to the exility of information about the real system. Some artifacts provided less information, 
    such as process videos, which only provide a limited perspective of the shop floor based on the camera's field of view and the skills of the video maker. 
    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues~\ref{fig:QualityInspectonResultsWithArtifacts}.
